### 2023-09-01 paper/sec-summary.tex
added funding and acknowledgements

\subsection*{Acknowledgments}
%
We are grateful to many colleagues involved in the Forward
Physics Facility initiative for many illuminating
discussions and encouragement along the course of this project.
%
We thank specially Felix Kling for may useful discussions in the course
of the project.
%
We thank Akitaka Ariga and Tomoko Ariga for discussion
concerning FASER$\nu$2, Milind Diwan,
Wenjie Wu and Steven Linden concerning FLArE,
and Antonia di Crescenzo concerning AdvSND.

>>>>

\subsection*{Acknowledgments}
%
We are grateful to many colleagues involved in the Forward
Physics Facility initiative for many illuminating
discussions and encouragement along the course of this project.
%
We thank specially Felix Kling for may useful discussions in the course
of the project and for providing the neutrino fluxes.
%
We thank Akitaka Ariga and Tomoko Ariga for discussion
concerning FASER$\nu$2, Milind Diwan,
Wenjie Wu and Steven Linden concerning FLArE,
and Antonia di Crescenzo concerning AdvSND. The work of M.F. was supported by NSF Grant PHY-2210283 and was also supported by NSF Graduate Research Fellowship Award No. DGE-1839285.
